---
title: "Weight of Fish"
author: "Valerie Rodriguez"
date: "'03/11/2023"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight


## Perch

```{r}
Fish <- read.csv(file= "Fish.csv", header=TRUE)
```

```{r}
Perch <- filter (Fish, Species=="Perch")
Perch <- select(Perch, -(Species))
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

### Best Two regressor model

Height and width is the best two regressor model from the chart above. This is because the adjusted r squared is the highest.

```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```

The best model and best 2 regressor model is the same being height and width.

##Five Element Perch Model
```{r}
best.Perch_Model <- lm(Weight ~ Height + Width, data = Perch)
five_element_Perch_model <- lm(Weight ~ .,data = Perch)
anova(best.Perch_Model, five_element_Perch_model)
```

The data shows that between the best perch model and the five element model there is no significant statistical difference. The p value is close to being 1.

This data(after added one perch model) shows that between best perch model and one perch model there is once again no significant statistical difference.


## Pike

```{r}
Pike <- filter (Fish, Species=="Pike")
Pike <- select(Pike, -(Species))
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topleft",main="Adjusted R^2")
```



### Best Two regressor model



## Roach


### Best Models


### Best Two regressor model


## Final Summary Statements
